---
title: " "
output: pdf_document
header-includes:
  - \usepackage{float}

bibliography: QP2.bib
csl: apa.csl
---

# Introduction

## Foreword

## Project Description

In South Africa, the forestry sector is increasingly seen as a critical sector for (i) livelihood development, given the simultaneous youth population bulge and high unemployment rates, as well as for (ii) the addressing of global sustainability challenges, given the potential of forestry to advance South Africa's National Climate Change Adaptation Plan (2018). Given this dual importance, Higher Education Institutions (HEIs) should naturally take a lead in preparing graduates to create sustainability-aligned economic opportunities. Yet, forestry HEIs in South Africa have constrained capacity to prepare graduates for post-school careers. These shortcomings exist for sector-specific knowledge on sustainable forestry practices, as well as for the entrepreneurial skills needed to leverage forestry opportunities. Given the importance of addressing these shortcomings, this project will involve collaboration between Finnish, Norwegian, and South African HEIs to develop the forestry-related curricula of South African HEIs, so that graduates are holistically equipped to sustainably leverage forestry for livelihood development.

The project will address:

-   Increasing levels of unemployment in South Africa.

    According to Statistics SA, South Africa experiences around 32.5% unemployment rate [@statssa2021]. Youth are the most vulnerable in the South African labour market, with even university graduates in this age group having an unemployment rate of 31.0%. Forestry-related entrepreneurship can provide a partial solution to this problem, as young people have enormous potential for innovation and risk-taking, which can produce start-ups employing many people. To fully realize these opportunities embedded in forestry, HEIs should use their curricula to produce inquisitive graduates who can think in new ways, and who have the courage to meet and adapt to the challenges facing them an entrepreneurial mindset that is simultaneously mindful of sustainability.

-   Foresters mitigating climate change.

    Forests are critical for global ecosystems and carbon balances, especially because of their potential to sequester carbon in forests. In its 2009 Forest Sector Charter, South Africa officially recognized its massive potential to sequester carbon through new afforestation of about 100 000 hectares (Forest Strategy 2009-2030). Yet, this potential has not been exploited, sustainability has not entered the mainstream of South African Forestry, and forestry graduates have not internalized the importance, benefits, and necessity of integrating sustainability into forestry. To address this shortcoming, climate-smart forestry will seek new ways of producing, using, and repurposing traditional forestry products like wood products, pulp, paperboard, and paper. This will include teaching forestry students the principles of the circular economy, of sustainable forestry management, and the potential of new innovative wood-based bioproducts. The overarching goal will be to not just lower the environmental impact of current forestry practices, but to leverage forestry management to increase the sequestration of carbon.

-   Foresters of 21st century, education shortcomings, and new teaching methods

    There is substantial discrepancy between what the forestry industry in South Africa sees as the key skills for future foresters, and what is being taught in HEIs offering forestry. Several research papers highlight this, as @längin2008 and @mgagaDoesTertiaryEducation2019. The higher education thus needs innovative approaches to develop 21st century foresters. To do this, South African HEIs will embrace teaching methods that not only improve information retention, but also allow students to learn how to solve real work problems. FOREST21 aims to assist a paradigm shift from teacher-centered knowledge sharing to the model where student create knowledge together for themselves (knowledge co-creation through discovery). In parallel, forestry HEIs will increase their curricula offerings on climate adaptation, and mainstream climate issues in core courses. Furthermore, HEIs need to recognize that they can serve as regional/local hubs for communities and business actors for creating, testing and disseminating knowledge and adaptation strategies.

-   Developing Entrepreneurial Mindsets

    21st century foresters need more than just forestry knowledge. Indeed, to leverage this knowledge effectively, they need an entrepreneurial mindset. This mindset will allow HEI graduates to identify, develop, exploit, and grow sustainability-related forestry opportunities, either through starting new ventures or through "intrapreneurship" in existing ventures. However, South African HEI's currently do little to develop these mindsets. As such, this project will work to develop entrepreneurial skills such as business plan development, while also focusing on the "softer" side of entrepreneurship so that graduates see entrepreneurship as a viable and beneficial employment pathway.

-   Forestry HEIs working together

    South African universities offering forestry currently do not work together. The mentality of working in silos has for a long-time been discouraged by industry government, but no change has been seen because there has not been a real opportunity for the HEIs to work together. Moreover, industry partners have sporadic cooperation with HEIs.

    However, this project will provide an opportunity for all forestry companies to work with all forestry HEIs. FOREST21 in unique as all existing, and two future, forestry HEIs are part of the consortia. Also, key stakeholders and governmental actors have committed to the project to create a framework for an impactful delivery.

### Target Groups

All partner HEIs have similar direct and indirect target groups with similar needs; thus target group identification and their needs analysis are presented jointly for all the Partner HEIs. The direct target groups: (i) students needing real-world relevant education, and (ii) HEIs needing to have the competence to deliver this.

-   The current **forestry graduates** are not equipped with skills and competencies to perform as expected in the world of work. This is one reason for the high unemployment of graduates. In addition, because the entrepreneurship curricula do not give entrepreneurial skills, graduates do not start businesses of their own. This means that forestry-sector potential is not utilized in societal development. Further, climate change and environmental challenges put pressure on forestry graduates' competences; they are to understand and to act through forestry for sustainability. Forestry21 aims to tackle the issue of curricula content and implementation relevancy in three of the Partner HEIs who will upgrade the current courses and in the two Partner HEIs will open new BSc forestry courses.

-   **Partner HEIs** have recognised the capacity gaps in curricula content and delivery methodology in their work to produce sustainable learning outcomes to support wealth creation and environmental sustainability. In South Africa, there are only random short courses on professional pedagogics available, and teachers have not been able to benefit training on how to plan and deliver curricula in a sustainable way. Forestry is the key leverage point for environmental sustainability and therefore needs to be integrated into the new and upgraded curricula.

-   **The university-industry partnership** is weak in all partner HEIs. To equip the graduates with work-life relevant skills and competences requires companies and NGOs/CBOs to be part of the learning ecosystem. Cooperation practises needs to be jointly developed and tested and after that institutionalized. Education governance needs good practises and research-based understanding on sustainable teaching and learning for the HEI quality enhancement.

### Expected Project Outcome

-   **Work-life responsive Climate Smart Forestry Curricula:** The curricula content is to meet the expectations of the world of work: students to be equipped with domain and metacognitive knowledge and skills to be attractive for employers, thus to be able to fulfil their respective mandates when employed. For this, graduates need (i) entrepreneurial mindset and practical entrepreneur competence which would even encourage them to establish businesses of their ow and (ii) comprehensive competencies for climate change mitigation through forestry.

-   **Skills development:** The partner HEI entrepreneurship curricula are concentrating on the knowledge component of competence, and the two other competence components - skills, and attitude development are both ignored. For entrepreneurial mindset building and expertise in environmental protection, skills development is crucial. The fundamental principle of competence is that competence only exists when all three parts of competence (knowing-doing-being) are present. The knowledge component is the easiest one to develop, and the skills development, where the learner applies the theory into practice, is the most challenging one. The being domain (attitude) naturally follows the skills component development; when being able to do, one develops self-confidence, the trust in him/herself and the right attitude to the work

-   **Authentic learning environment:** The skills development is not possible without real-life experiences. The authentic learning environment is critical for internalizing both climate-smart forestry and sustainability. The collaborative learning ecosystem where forestry community, industry and communities are part of the learning and teaching process, is a motivating and transformative way of learning. In challenge-driven learning, students are invited to read and analyse the problem scenario, absorb and analyse information, work in teams to use creativeness and innovation, develop possible actions and present the findings. In this self-directive learning process, students take responsibility for their own learning and the teacher serves as a resource to the student teams. The skills development increases students' competitiveness in the world of work and relevance to the labour market. Also, it develops students' domain-specific knowledge and their understanding of their professional identity. For the challenge-owners the collaborative learning ecosystem brings benefits as well; at its best, they get innovative and creative solutions and in every case, they get new members to their community of practice.

-   **21st-century skills:** Students of today are preparing themselves to the world of work which is constantly changing and different tomorrow than today. The domain-specific knowledge is not enough for the graduates to be qualified to meet the requirement of the future world of work. 21st-century skills emphasise critical thinking & problem solving, innovativeness & creativeness and teamwork & communication, leadership skills, self-directiveness, cross-cultural and diversity competences, lifelong learning skills and high work ethics. All of these are topics the curricula must contain. The collaborative skills development process with real-life cases contributes to developing all these metacognitive competences of future professionals.

### Project Goals and Objectives

Despite the huge potential, South Africa (SA) is having challenges to create forestry-based jobs and wealth. At the same time strong forestry expertise is needed to fulfill the national climate change/carbon commitments. One very critical reason for the forestry-sector not meeting its expectations in societal and environmental development is that the skills and competences of HEI forestry-graduates do not match the requirements of the world of work. Changing this situation requires:

-   Cooperation between academia and societal/industry partners

-   A new approach in HEIs for producing the new and critical competencies

-   HEIs to be equipped with 21st century forestry competences

#### Wider Objective

> ***Strengthening South African forestry HEIs capacity to provide work-life relevant and inclusive higher education for societal and environmental development.***

#### FOREST21 Specific Objectives

1.  Utilization of new climate smart forestry curricula with incorporation of entrepreneurial skills and metacognitive competences

2.  Improved student-centered teaching and learning methods by introducing problem-based learning

3.  Actively cooperating network-based learning ecosystem with academia and societal/industry partners in South African context

4.  Strengthened HEI capacity to further contextualize and develop curricula, pedagogical methodology and learning ecosystems through national and international partnerships

### Project Coordinator

### Participating Organizations

```{r participants, echo = FALSE}

library(flextable)
library(magrittr)

set_flextable_defaults(fonts_ignore=TRUE) 

participants <- data.frame(Institution = c("Fort Cox Agriculture and Forestry Training Institute", "Nelson Mandela University", "Tschwane University of Technology", "Stellenbosch University", "University of Venda", "Häme University of Applied Sciences", "Inland Norway University of Applied Sciences", "Aalto University"),                                
                         Abbr = c("Fort Cox", "NMU", "TUT", "SU", "UNIVEN", "HAMK", "INN", "Aalto"),
                         Description = c("Established in 1930, the only SA institution offering Diplomas in Forestry; visions is to be the leading center in sustainable agriculture and forestry by providing quality education and training in agriculture and forestry, by engaging to applied research and community outreach with final objective to improve livelihood in SA.", "Roots back to 1911, when the oldest forestry campus of SA was established to Tokai near Cape Town. Todau NMU, after several mergers and name changes, has a proud tradition of excellence and service to the forestry industry.", "Established in 2003 through several mergers; defines itself as a people’s university that makes knowledge work. Strategic Plan 2020-25 wants TUT learning to become a continuum of creation, innovation and technology transfer to serve the communities; to find authentic and enduring solutions to communities’ most pressing problems.", "The oldest university in South Africa; received full university status in 1918. SU wants to be research-intensive university which attracts outstanding students, employ talented staff and provide a world-class environment; a place connected to the world, while enriching and transforming local, continental and global communities.", "Opened in 1982 to cater for the then Homeland of Venda; since its establishment, the UNIVEN has experienced tremendous growth and change and to date the university has established itself as a national asset through its niche on problem oriented, project-based curriculum with a strength in nurturing under prepared students into nationally competitive graduates.", "Häme University of Applied Sciences (HAMK) is a multidisciplinary, workplace-orientated higher education institution. HAMK offers 27 Bachelor’s degree programmes, 10 Master’s degree programmes and professional teacher education. Ten of the degree programmes are taught in English.", "INN is a result of the 2017 merger of two academic institutions with long traditions. It now runs 6 campuses with a total of 16,000 students on a vast range of study programs, including 4 PhD programs.", "By merging three leading Finnish universities in 2010, Aalto was founded to work as a societally embedded research university. In a short space of time, Aalto University has since become a forerunner in our key areas. We are renowned for our sense of community and culture of entrepreneurship and innovation."))

participants <- flextable(participants)
participants <- set_caption(participants, "Participating Organizations")

participants <- height(participants, height = .3) %>% 
  hrule(rule = "exact", part = "body")  
                       
participants %>%  
  theme_vanilla() %>% # evt theme_zebra
  width(j=~Institution,width=1) %>% 
  width(j=~Abbr,width=0.6) %>%
  width(j=~Description, width = 5)
  
```

### Project Characteristics

### Work Packages

```{r WP, echo = FALSE}

library(flextable)
library(magrittr)

set_flextable_defaults(fonts_ignore=TRUE) 

workpackages <- data.frame(WP = c("WP1",
                                  "WP2",
                                  "WP3",
                                  "WP4",
                                  "WP5"),                                
                           Lead = c("SU",
                                   "NMU",
                                   "INN",
                                   "TUT",
                                   "HAMK"),
                          Co_Lead = c("NMU",
                                      "TUT, UNIVEN, Aalto",
                                      "SU, UNIVEN, Fort Cox",
                                      "Fort Cox, SU",
                                      ""),
                          Content = c("Foundation for paradigm change FOREST21 Curricula with entrepreneurship competence                                          + soft skills integration. Creation of joint understanding PBL + Climate Smart                                           Forestry Curricula and build HEI ownership to the transformation.",
                                      "Trainings on PBL-method and contextualizing it through field-challenges; knowledge                                          creation of climate smart forestry; setting up structures for the project                                                sustainability and further methodological development.",
                                      "PAR-based quality assurance of the project implementation and management.",
                                      "Dissemination and exploitation; project information",
                                      "Functional and participatory project management structures"))

workpackages <- flextable(workpackages)
workpackages <- set_caption(workpackages, "Work Packages")

workpackages <- height(workpackages, height = .3) %>% 
  hrule(rule = "exact", part = "body")  
                       
workpackages %>%  
  theme_vanilla() %>% # evt theme_zebra
  width(j=~WP,width=0.5) %>% 
  width(j=~Lead,width=0.5) %>%
  width(j=~Co_Lead, width=1.6) %>%
  width(j=~Content, width=4)
  
```

```{r WP1details, echo = FALSE}

library(flextable)
library(magrittr)

set_flextable_defaults(fonts_ignore=TRUE) 

wp1details <- data.frame(Activities = c("Feasibility Study on PBL /pedagogical competence and knowledge on climate smart forestry to define the Partner HEIs’ institutional and individual gaps and stakeholder mapping. Incl. HBRA/Gender.",    "Curricula development workshop to set up the contextualized PBL frame, FOREST21 Curricula methodology & development and training needs collaborative learning ecosystem building (community of praxis). European partners will share their knowledge of competence-bases methods. Following the workshop, the adaptation of PBL to the new FOREST21 Curricula/development of new PBL-based curricula is done.", "Curricula developed (2) and up-graded (5): all Partner HEIs."),                                
                         Time = c("Report prepared; time 1-9/21.", "9/21", "Accredited by end of 2022."))

wp1details <- flextable(wp1details)
wp1details <- set_caption(wp1details, "WP 1 - Activities")

wp1details <- height(wp1details, height = .3) %>% 
  hrule(rule = "exact", part = "body")  
                       
wp1details %>%  
  theme_vanilla() %>% # evt theme_zebra
  width(j=~Activities,width=5) %>% 
  width(j=~Time,width=2)
  
```

```{r WP2details, echo = FALSE}

library(flextable)
library(magrittr)

set_flextable_defaults(fonts_ignore=TRUE) 

wp2details <- data.frame(Activities = c("Pedagogical training workshop I and II: teaching methods (PBL, ODL), guidance on students’ field cases and competence-based assessment, collaborative learning ecosystem building, field challenge preparation.", "Climate Smart Forestry workshop: Associate Partner participation encouraged (own cost)", "Web-based support for pedagogical and climate smart forestry development provided. All partners before and after capacity building workshops.", "Pedagogical and climate smart forestry workshop training materials developed, incl. digi.", "Establishment of societal/industry partnerships (min 5/Partner): all Partner HEIs.", "Student challenges (total 195 students): Students from all Project countries participate and based on the interest of students and needs of the case, diverse student teams are formed. Field challenges are organized in unison with the PBL- workshops to save in travel costs. Student challenges are built and formulated around the Partner HEIs local partnerships. Teachers and faculty staff from all partners supervise jointly the challenges and fieldwork.", "PBL-FOREST21 Teacher Manual prepared: all partners", "PBL-FOREST21 Network with min. 50 members established"),                                
                        Time = c("Number of Partner HEI staff/faculty trained 50, number of Programme country trainers 12. 2/22 UNIVEN and NMU 9/22", "Number of Partner HEI staff/faculty trained 25, number of Programme country trainers 8. 5/22", "By 1/22-8/22", "By 8/22.", "By 11/22", "All Partner HEI: Total number of Partner country students 150, Programme country students 45. 2-3/22, 9-10/22, 2-3/23", "By 8/23", "By 8/23"))

wp2details <- flextable(wp2details)
wp2details <- set_caption(wp2details, "WP 2 - Activities")

wp2details <- height(wp2details, height = .3) %>% 
  hrule(rule = "exact", part = "body")  
                       
wp2details %>%  
  theme_vanilla() %>% # evt theme_zebra
  width(j=~Activities,width=5) %>% 
  width(j=~Time,width=2)
  
```

```{r WP3details, echo = FALSE}

library(flextable)
library(magrittr)

set_flextable_defaults(fonts_ignore=TRUE) 

wp3details <- data.frame(Activities = c("PAR-Quality Plan (QP) prepared and Quality Platform set up. QP defines scheduled quality assurance activities with objectives, roles, and responsibilities. Included HBRA/Gender Action Plan + Check list. Quality Management Platform used for data collection and reporting.", "Quality data collection and analysis.", "Web-based support for pedagogical and climate smart forestry development provided. All partners before and after capacity building workshops.", "Project QP and process used to upgrade Partner HEIs’ education quality management"),                                
                        Time = c("By 8/21", "2-3/22 and 6-7/23", "9/23", "By 8/22."))

wp3details <- flextable(wp3details)
wp3details <- set_caption(wp3details, "WP 3 - Activities")

wp3details <- height(wp3details, height = .3) %>% 
  hrule(rule = "exact", part = "body")  
                       
wp3details %>%  
  theme_vanilla() %>% # evt theme_zebra
  width(j=~Activities,width=5) %>% 
  width(j=~Time,width=2)
  
```

```{r WP4details, echo = FALSE}

library(flextable)
library(magrittr)

set_flextable_defaults(fonts_ignore=TRUE) 

wp4details <- data.frame(Activities = c("Dissemination & Exploitation Plan (DEP) developed; Covers time from the project start beyond project exit. DEP guides dissemination during and at the end of the Project SMART indicators prepared and used for measuring D&E efficiency D&E Manager with Partners", "Internal Project information channels and working platforms established and in function, incl. HEIs students’ and staffs’ information", "Forestry South Africa (FSA) and Associate Partners heavily involved and support", "Project information to key stakeholders", "Publications (min 5) and conference papers (min 5)", "Final seminar: to present the Project results to a broader audience including public and private forestry sector, NGOs, student communities, and national & regional education managers"),                                
                        Time = c("by 8/21", "1/21-12/23", "21-12/23 and beyond the Project exits", "", "by 11/23", "9/23"))

wp4details <- flextable(wp4details)
wp4details <- set_caption(wp4details, "WP 4 - Activities")

wp4details <- height(wp4details, height = .3) %>% 
  hrule(rule = "exact", part = "body")  
                       
wp4details %>%  
  theme_vanilla() %>% # evt theme_zebra
  width(j=~Activities,width=5) %>% 
  width(j=~Time,width=2)
  
```

```{r WP5details, echo = FALSE}

library(flextable)
library(magrittr)

set_flextable_defaults(fonts_ignore=TRUE) 

wp5details <- data.frame(Activities = c("Setting up the project modalities: LCs, Project Management Team, Advisory Board, partnership agreements singed. Project Management Guidelines incl. finance, prepared & project management practices developed", "Kick-off meeting organised", "Mid-term review and Final evaluation + audit", "Interim and Final reports"),                                
                        Time = c("", "3/21", "5-7/22 and 9-12/23", ""))

wp5details <- flextable(wp5details)
wp5details <- set_caption(wp5details, "WP 5 - Activities")

wp5details <- height(wp5details, height = .3) %>% 
  hrule(rule = "exact", part = "body")  
                       
wp5details %>%  
  theme_vanilla() %>% # evt theme_zebra
  width(j=~Activities,width=5) %>% 
  width(j=~Time,width=2)
  
```

### Regulatory Framework and References

### Structure for Project Work and Cooperation

### Key Project Deliverables, Milestones and Processes

## Definitions

### Quality Management

### Quality Planning

### Quality Assurance

### Quality Control
